An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-08-01 EconGrowth.Rnw
Narrowed limits on CES resample plots with sigmas to the range (0, 2.5).

<<CES_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType=NA) + ylim(0, 2)
@

@@

Coefficients for each resampled CES model (with $q$)
are shown in 
Figures~\ref{fig:CESq_lambda_gamma_Cloud_Graph}--\ref{fig:CESq_sigma_delta_Cloud_Graph}.

<<CESq_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$) resample model parameters $\\lambda$ and $\\gamma$.">>=
cesResamplePlotLambdaGamma(energyType="Q")
@

<<CESq_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="Q")
@

<<CESq_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="Q")
@

Coefficients for each resampled CES model (with $x$)
are shown in 
Figures~\ref{fig:CESx_lambda_gamma_Cloud_Graph}--\ref{fig:CESx_sigma_delta_Cloud_Graph}.

<<CESx_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$) resample model parameters $\\lambda$ and $\\gamma$.">>=
cesResamplePlotLambdaGamma(energyType="X")
@

<<CESx_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="X")
@

<<CESx_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="X")
@

Coefficients for each resampled CES model (with $u$)
are shown in 
Figures~\ref{fig:CESu_lambda_gamma_Cloud_Graph}--\ref{fig:CESu_sigma_delta_Cloud_Graph}.

<<CESu_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$) resample model parameters $\\lambda$ and $\\gamma$.">>=
cesResamplePlotLambdaGamma(energyType="U")
@

<<CESu_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="U")
@

<<CESu_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="U")
@

Figure~\ref{fig:CESq_Params_Graph} shows values and 95\% confidence intervals 
for the parameters for the CES model (with $q$).

<<CESq_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with $q$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
createCESParamsGraph(energyType="Q")
@

@@

<<CESx_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with $x$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
createCESParamsGraph(energyType="X")
@

@@

<<CESu_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with $u$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
createCESParamsGraph(energyType="U")
@

@@

<<CES_GDP_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES results.">>=
createCESLatticeGraph()
@

@@

<<LINEXq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with $q$) resampling results.">>=
# linexResamplePlot(energyType="Q")
linexResamplePlot(energyType="Q")
@

<<LINEXx_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with $x$) resampling results.">>=
linexResamplePlot(energyType="X")
@

>>>>

<<CES_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType=NA) + ylim(0, 2.5)
@

@@

Coefficients for each resampled CES model (with $q$) for the ($kl$)$e$ nesting
are shown in 
Figures~\ref{fig:CESq_lambda_gamma_Cloud_Graph_kle}--\ref{fig:CESq_sigma_delta_Cloud_Graph_kle}.

<<CESq_lambda_gamma_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($kl$)$e$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
cesResamplePlotLambdaGamma(energyType="Q", nest="(kl)e")
@

<<CESq_sigma_1_delta_1_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($kl$)$e$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(kl)e") + ylim(0, 2.5)
@

<<CESq_sigma_delta_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($kl$)$e$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="Q", nest="(kl)e") + ylim(0, 2.5)
@

Coefficients for each resampled CES model (with $x$, ($kl$)$e$ nesting)
are shown in 
Figures~\ref{fig:CESx_lambda_gamma_Cloud_Graph_kle}--\ref{fig:CESx_sigma_delta_Cloud_Graph}.

<<CESx_lambda_gamma_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($kl$)$e$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
cesResamplePlotLambdaGamma(energyType="X", nest="(kl)e")
@

<<CESx_sigma_1_delta_1_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($kl$)$e$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="X", nest="(kl)e") + ylim(0, 2.5)
@

<<CESx_sigma_delta_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($kl$)$e$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="X", nest="(kl)e") + ylim(0, 2.5)
@

Coefficients for each resampled CES model (with $u$)
are shown in 
Figures~\ref{fig:CESu_lambda_gamma_Cloud_Graph_kle}--\ref{fig:CESu_sigma_delta_Cloud_Graph_kle}.

<<CESu_lambda_gamma_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($kl$)$e$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
cesResamplePlotLambdaGamma(energyType="U", nest="(kl)e")
@

<<CESu_sigma_1_delta_1_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($kl$)$e$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="U", nest="(kl)e") + ylim(0, 2.5)
@

<<CESu_sigma_delta_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($kl$)$e$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="U", nest="(kl)e") + ylim(0, 2.5)
@

Coefficients for each resampled CES model (with $q$) for the ($le$)$k$ nesting
are shown in 
Figures~\ref{fig:CESq_lambda_gamma_Cloud_Graph_lek}--\ref{fig:CESq_sigma_delta_Cloud_Graph_lek}.

<<CESq_lambda_gamma_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($le$)$k$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
cesResamplePlotLambdaGamma(energyType="Q", nest="(le)k")
@

<<CESq_sigma_1_delta_1_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($le$)$k$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(le)k") + ylim(0, 2.5)
@

<<CESq_sigma_delta_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($le$)$k$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="Q", nest="(le)k") + ylim(0, 2.5)
@

Coefficients for each resampled CES model (with $x$ and ($le$)$k$ nesting)
are shown in 
Figures~\ref{fig:CESx_lambda_gamma_Cloud_Graph_lek}--\ref{fig:CESx_sigma_delta_Cloud_Graph_lek}.

<<CESx_lambda_gamma_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($le$)$k$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
cesResamplePlotLambdaGamma(energyType="X", nest="(le)k")
@

<<CESx_sigma_1_delta_1_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($le$)$k$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="X", nest="(le)k") + ylim(0, 2.5)
@

<<CESx_sigma_delta_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($le$)$k$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="X", nest="(le)k") + ylim(0, 2.5)
@

Coefficients for each resampled CES model (with $u$ and ($le$)$k$ nesting)
are shown in 
Figures~\ref{fig:CESu_lambda_gamma_Cloud_Graph_lek}--\ref{fig:CESu_sigma_delta_Cloud_Graph_lek}.

<<CESu_lambda_gamma_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($le$)$k$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
cesResamplePlotLambdaGamma(energyType="U", nest="(le)k")
@

<<CESu_sigma_1_delta_1_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($le$)$k$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="U", nest="(le)k") + ylim(0, 2.5)
@

<<CESu_sigma_delta_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($le$)$k$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="U", nest="(le)k") + ylim(0, 2.5)
@

Coefficients for each resampled CES model (with $q$) for the ($ek$)$l$ nesting
are shown in 
Figures~\ref{fig:CESq_lambda_gamma_Cloud_Graph_ekl}--\ref{fig:CESq_sigma_delta_Cloud_Graph_ekl}.

<<CESq_lambda_gamma_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($ek$)$l$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
cesResamplePlotLambdaGamma(energyType="Q", nest="(ek)l")
@

<<CESq_sigma_1_delta_1_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($ek$)$l$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(ek)l") + ylim(0, 2.5)
@

<<CESq_sigma_delta_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($ek$)$l$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="Q", nest="(ek)l") + ylim(0, 2.5)
@

Coefficients for each resampled CES model (with $x$ and ($ek$)$l$ nesting)
are shown in 
Figures~\ref{fig:CESx_lambda_gamma_Cloud_Graph_ekl}--\ref{fig:CESx_sigma_delta_Cloud_Graph_ekl}.

<<CESx_lambda_gamma_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($ek$)$l$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
cesResamplePlotLambdaGamma(energyType="X", nest="(ek)l")
@

<<CESx_sigma_1_delta_1_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($ek$)$l$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="X", nest="(ek)l") + ylim(0, 2.5)
@

<<CESx_sigma_delta_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($ek$)$l$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="X", nest="(ek)l") + ylim(0, 2.5)
@

Coefficients for each resampled CES model (with $u$ and ($ek$)$l$ nesting)
are shown in 
Figures~\ref{fig:CESu_lambda_gamma_Cloud_Graph_ekl}--\ref{fig:CESu_sigma_delta_Cloud_Graph_ekl}.

<<CESu_lambda_gamma_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($ek$)$l$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
cesResamplePlotLambdaGamma(energyType="U", nest="(ek)l")
@

<<CESu_sigma_1_delta_1_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($ek$)$l$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="U", nest="(ek)l") + ylim(0, 2.5)
@

<<CESu_sigma_delta_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($ek$)$l$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="U", nest="(ek)l") + ylim(0, 2.5)
@

Figure~\ref{fig:CESq_Params_Graph} shows values and 95\% confidence intervals 
for the parameters for the CES model (with $q$, ($kl$)$e$ nesting).

<<CESq_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with $q$, ($kl$)$e$ nesting) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
createCESParamsGraph(energyType="Q")
@

@@

<<CESx_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with $x$, ($kl$)$e$ nesting) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
createCESParamsGraph(energyType="X")
@

@@

<<CESu_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with $u$, ($kl$)$e$ nesting) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
createCESParamsGraph(energyType="U")
@

@@

<<CES_GDP_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES results (($kl$)$e$ nesting).">>=
createCESLatticeGraph()
@

@@

<<LINEXq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with $q$) resampling results.">>=
# linexResamplePlot(energyType="Q")
linexResamplePlot(energyType="Q") + ylim(-20, 10)
@

<<LINEXx_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with $x$) resampling results.">>=
linexResamplePlot(energyType="X") + ylim(-20, 10)
@
